%!TEX root = main.tex
\section{Motivation}
\label{sec:motivation}
The assessment of software quality is one of the most multifaceted (\eg structural, product, and quality) and subjective aspects of software engineering (since in many cases it is substantially based on expert judgement).
Such assessments can be performed at almost all the phases of software development (from project inception to maintenance) and at different levels of granularity (from source code to architecture).
However, human judgement is inherently biased by implicit, subjective criteria applied to the evaluation process, and its economical effectiveness is limited compared to automated or semi-automated approaches.
To this end, researchers are still looking for new and more effective methods for assessing various qualitative characteristics of software systems and the related processes.
In recent years, we have been observing a rising interest in adopting various approaches to exploiting machine learning and automated decision-making processes in several areas of software engineering.
The machine learning models and algorithms help to reduce effort and risk related to human judgment in favor of automated systems, which are able to make informed decisions based on available data and evaluated with objective criteria.
Therefore, the adoption of machine learning techniques seems to be one of the most promising ways to improve software quality evaluation.
Conversely, learning capabilities are increasingly embedded within software, including in critical domains such as automotive and health.
For this reason, the application of quality assurance techniques is required to ensure the reliable engineering of software systems based on machine learning.
After the successful past editions of the workshop on Machine Learning Techniques for Software Quality Evaluation (MaLTeSQuE), which have been held:
\begin{enumerate}
    \item in Klagenfurt (Austria) on February 21$^{st}$, 2017,
    \item collocated with SANER 2017 in Campobasso (Italy) on March 23$^{rd}$ , 2018,
    \item collocated with SANER 2018, and in Tallin (Estonia) on August 27$^{th}$ 2019,
    \item collocated with ESEC/FSE 2019,
\end{enumerate}
we propose a novel edition of the workshop.
