%!TEX root = main.tex

\section{Organizers}

The organizers are all researchers with a software engineering and machine learning background.
We propose a team composed by a senior member, \ie Prof. Foutse Khom and junior members, \ie Dr. Gemma Catolino, and Dr. Pasquale Salza.

\label{sec:organizers}
\subsection{Gemma Catolino}
Dr. Gemma Catolino is a post-doctoral researcher at the Delft University of Technology, the Netherlands.
In 2020, she received the European Ph.D. Degree from the University of Salerno, Italy.
Her research interests include human factors in software maintenance and evolution, empirical software engineering, source code quality, and mining software repositories.
She serves and has served as a program committee member of various international conferences and as referee for flagship journals in the fields of software engineering.
She received the best Master's thesis award from the Italian Software Metrics Association in 2016 and a gold medal for the Microsoft Student Research Competition in 2018 at the IEEE/ACM International Conference on Mobile Software Engineering and Systems.\\
Contact her at: \href{mailto:g.catolino@tudelft.nl}{g.catolino@tudelft.nl}.\\
More info at: \url{https://www.gemmacatolino.com}


\subsection{Pasquale Salza}
Dr. Pasquale Salza is a Senior Research Associate at the University of Zurich, Switzerland.
His research interests include on software engineering, cloud computing, evolutionary computation, machine learning, and mobile computing.
Salza received a Ph.D. degree in Computer Science from the University of Salerno, Italy.\\
Contact him at: \href{mailto:salza@ifi.uzh.ch}{salza@ifi.uzh.ch}.\\
More info at: \url{https://pasqualesalza.com}

\subsection{Foutse Khomh}
Foutse Khomh is a Professor of Software Engineering at Polytechnique Montréal and FRQ-IVADO Research Chair on Software Quality Assurance for Machine Learning Applications. He received a Ph.D in Software Engineering from the University of Montreal in 2010, with the Award of Excellence. He also received a CS-Can/Info-Can Outstanding Young Computer Science Researcher Prize for 2019. His research interests include software maintenance and evolution, machine learning systems engineering, cloud engineering, empirical software engineering, and software analytic. His work has received three ten-year Most Influential Paper (MIP) Awards, and five Best/Distinguished paper Awards. He has served on the program committees of several international conferences including FSE, ICSM(E), SANER, MSR, ICPC, SCAM, ESEM and has reviewed for top international journals such as JSS, EMSE, TSC, TSE and TOSEM. He is program chair for Satellite Events at SANER 2015, program co-chair of SCAM 2015, ICSME 2018, PROMISE 2019, and ICPC 2019, general chair of ICPC 2018, SCAM 2020, and SANER 2020. He is on the steering committee of SANER (chair), MSR, PROMISE, ICPC (chair), and ICSME(vice-chair). He initiated and co-organized the Software Engineering for Machine Learning Applications (SEMLA) symposium (https://semla.polymtl.ca/) and the RELENG (Release Engineering) workshop series (http://releng.polymtl.ca). He is an Associate Editor for IEEE Software.\\
Contact him at: \href{mailto:foutse.khomh@polymtl.ca}{foutse.khomh@polymtl.ca}.\\
More info at: \url{http://www.khomh.net/}\\
He acts as the main contact.
