%!TEX root = main.tex
\section{Paper selection procedure}
\label{sec:submissions}

We are looking for two different types of papers; the first one, \ie technical papers, where we invite to submit original research (even at early stages of evaluation) on how machine learning and software quality assurance can support each other.
Papers must not exceed 6 pages for the main text, including figures, tables, appendices, and references.
They will be part of the ESEC/FSE proceedings under the copyright of the ACM digital library and available for participants in advance through a workshop webpage.

The second one, \ie presentation abstracts, which have to report the research results that have already been published, or that are ready to be submitted to a conference or a journal.
They will only be reviewed for relevance, and will not be included in the MaLTeSQuE proceedings.
When accepted, the 2 pages will be made available on the website of the workshop.

We expect industrial practitioners to submit summaries on the use of machine learning for software quality or the validation and verification of systems based on machine learning, with the purpose of stimulating the discussion, initiate challenging new avenues, etc.

All papers should be submitted in the PDF format, conforming to the ACM conferences template, through HotCRP.com.
To attract participants for this workshop, we will distribute its call for paper in mailing lists related to the communities of software engineering and machine learning.

\subsection{Review Process}
The process for paper submission and evaluation will be similar to the ESEC/FSE one.
Therefore, all submitted papers will undergo a rigorous peer review process, with emphasis on their originality, quality, soundness and relevance.
In the same way as ESEC/FSE, the workshop will follow a double-blind review process, where three program committee members will review each submitted paper.
Afterwards, the program committee will jointly make the final decision concerning the acceptance of individual papers, based on the reviews.

\subsection{Expected Dates}
For the expected dates for submission, we conform to the ESEC/FSE 2020 indications:
\begin{itemize}[itemsep=0.5em]
	\item Submission July 8$^{th}$, 2020
	\item Notification Aug 26$^{th}$, 2020
\end{itemize}


\subsection{Confirmed Program Committee Members}
The program committee members are selected among both senior and junior researchers working on the topics of the workshop with the aim of (a) ensuring a high review quality, (b) supporting the emergence of junior researchers in the community and attract established researchers from communities related to artificial intelligence and machine learning.
We are still recruiting program committee members, some of them already accepted the invitation, however, there are other members that nicely served as referees in the last editions of the workshop and we are confident that they will accept again our invitation.\\
The confirmed program committee members are:
\begin{itemize}[itemsep=0.5em]
	
	\item Mathieu Acher, University of Rennes I
	\item Francesca Arcelli Fontana, University of  Milano Bicocca
	\item Apostolos Ampatzoglou, University of Macedonia
	\item Dario Di Nucci, Jheronimus Academy of Data Science
	\item Bartosz Walter, Poznan University of Technology
	\item Maxime Cordy, University of Luxembourg
	\item Valerio Terragni, USI Università della Svizzera italiana
	\item Gemma Catolino, Delft University of Technology
	\item Pasquale Salza, University of Zurich
	\item Foutse Khom, Polytechnique Montréal
	\item Fabio Palomba, University of Salerno
	\item Gilles Perrouin, University of Namur
	\item Damian A. Tamburri, Jheronimus Academy of Data Science
	\item Davide Taibi, Tampere University
	\item Valentina Lenarduzzi, Tampere University
	\item Xavier Devroey, Delft University of Technology
	\item Luís Cruz, Delft University of Technology
	\item Giovanni Grano, University of Zurich
    
	
\end{itemize}
	
	while the prospective program committee members are

\begin{itemize}[itemsep=0.5em]
	
	
	\item Rémi Emonet, Laboratoire Hubert Curien
	\item Daniel Feitosa, University of Groningen
    \item David Lo, Singapore Management University
	\item Benoit Frenay, University of Namur
	\item Suman Jana, Columbia University
    \item George Kakarontzas, Tech. Educ. Inst. of Thessaly
	\item Marta Kwiatkowska, University of Oxford
	\item Lech Madeyski, Wroclaw University of Technology
    \item Lei Ma, Kyushu University
	\item Karl Meinke, KTH Royal Institute of Technology
	\item Tim Menzies, NC State University
	\item Elvira-Maria Arvanitou, University of Macedonia
	\item Earl T. Barr, University College London
	\item Stamatia Bibi, University of Western Macedonia
	\item Jordi Cabot, Open University of Catalonia
	\item Alexander Chatzigeorgiou, University of Macedonia
	\item Jurgen Cito, Wien University of Technology
	\item Eleni Constantinou, Eindhoven University of Technology
	\item Steve Counsell, Brunell University
	\item Jesse Davis, Katholieke Universiteit Leuven
	\item Mirosław Ochodek, Poznan University
	\item Haidar Osman, University of Bern
	\item Annibale Panichella, Delft University of Technology
	\item Sebastiano Panichella, University of Zurich
	\item Jean-Francois Raskin, University Libre de Bruxelles
	\item Koushik Sen, University of California, Berkeley
	\item Alyson Smith, Decisive Analytics Corporation
	\item Paolo Tonella, University della Svizzera italiana
	\item Yves Le Traon, University of Luxembourg
	\item Aiko Yamashita, Oslo University

\end{itemize}
